---
title: "Industry purpose"
author: "Kirk-Mends Attafuah"
date: "2025-12-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





All Data

```{r}

library(data.table)  # fread, rbindlist
library(dplyr)       # dplyr verbs
library(stringr)     # str_extract, str_detect
library(readr)       # read_csv
library(pracma)      # findpeaks
library(tidyr)       # pivoting if needed


base_folder <- "C:/Users/kirkm/Music/My research works/Engineering/SenseCobot/SenseCobot"


# Helper functions


# Parse filename into metadata
parse_filename <- function(path) {
  fname <- basename(path)
  
  # Detect baseline vs task
  if (str_detect(fname, regex("Baseline", ignore_case = TRUE))) {
    task_clean <- "Baseline"
  } else {
    task_clean <- str_extract(fname, regex("Task\\s*\\d+", ignore_case = TRUE))
  }
  
  tibble(
    file = path,
    Participant = str_extract(fname, "P_\\d+"),   # captures P_02, P_03, … P_21
    Task = task_clean
  )
}

# Read file + attach metadata
read_with_meta <- function(meta_row) {
  df <- read_csv(meta_row$file, show_col_types = FALSE)
  if ("Timestamp" %in% names(df)) {
    df <- df %>% mutate(Timestamp = as.character(Timestamp))
  }
  df %>%
    mutate(
      Participant = meta_row$Participant,
      Task = meta_row$Task
    )
}


# Process folder with metadata
process_folder <- function(folder_path) {
  files <- list.files(folder_path, pattern = "\\.csv$", full.names = TRUE)
  if (length(files) == 0) return(tibble())
  
  meta <- bind_rows(lapply(files, parse_filename))
  
  all_data <- bind_rows(lapply(1:nrow(meta), function(i) {
    row <- meta[i, ]
    read_with_meta(as.list(row))
  }))
  
  all_data
}


# RMSSD functions

compute_rmssd_from_ecg <- function(ecg_signal, sampling_rate = 250) {
  if (length(ecg_signal) < sampling_rate * 5) return(NA_real_)
  z <- (ecg_signal - mean(ecg_signal, na.rm = TRUE)) / sd(ecg_signal, na.rm = TRUE)
  peaks <- findpeaks(z,
                     minpeakheight = 1.0,
                     minpeakdistance = round(sampling_rate * 0.28))
  if (is.null(peaks)) return(NA_real_)
  r_peak_indices <- peaks[,2]
  ibi <- diff(r_peak_indices) / sampling_rate
  if (length(ibi) < 3) return(NA_real_)
  sqrt(mean(diff(ibi)^2, na.rm = TRUE))
}

compute_rmssd_from_ibi <- function(ibi_vector) {
  if (length(ibi_vector) < 3) return(NA_real_)
  sqrt(mean(diff(ibi_vector)^2, na.rm = TRUE))
}

ibi_to_sdnn <- function(ibi_vector) sd(ibi_vector, na.rm = TRUE)
ibi_to_mean_hr <- function(ibi_vector) mean(60 / ibi_vector, na.rm = TRUE)


# Load raw data (industry realistic)

eda_data <- process_folder(file.path(base_folder, "EDA_Empatica_Signals"))
hr_data  <- process_folder(file.path(base_folder, "HR_Bangle_Signals"))
ibi_data <- process_folder(file.path(base_folder, "IBI_Empatica_Signals"))
ecg_data <- process_folder(file.path(base_folder, "ECG_Shimmer3_Signals"))


# Aggregate features

# Function to compute SCR features from EDA
compute_scr_features <- function(eda_signal, min_height = 0.05, min_distance = 1) {
  if (length(eda_signal) < 10) return(list(SCR_count = NA, SCR_mean_amp = NA))
  
  # Normalize or detrend if needed
  eda_norm <- eda_signal - min(eda_signal, na.rm = TRUE)
  
  # Find peaks
  peaks <- findpeaks(eda_norm,
                     minpeakheight = min_height,
                     minpeakdistance = min_distance)
  
  if (is.null(peaks)) {
    return(list(SCR_count = 0, SCR_mean_amp = 0))
  } else {
    SCR_count <- nrow(peaks)
    SCR_mean_amp <- mean(peaks[,1], na.rm = TRUE)  # peak heights
    return(list(SCR_count = SCR_count, SCR_mean_amp = SCR_mean_amp))
  }
}

     
# EDA + ACC + HR + TEMP
eda_task <- eda_data %>%
  group_by(Participant, Task) %>%
  summarise(
    EDA_median   = median(EDA, na.rm = TRUE),
    EDA_mean     = mean(EDA, na.rm = TRUE),
    EDA_sd       = sd(EDA, na.rm = TRUE),
    ACC_vm_mean  = mean(sqrt(ACC_X^2 + ACC_Y^2 + ACC_Z^2), na.rm = TRUE),
    ACC_vm_sd    = sd(sqrt(ACC_X^2 + ACC_Y^2 + ACC_Z^2), na.rm = TRUE),
    HR_median    = median(HR, na.rm = TRUE),
    TEMP_median  = median(TEMP, na.rm = TRUE),
    # New SCR features
    SCR_count    = compute_scr_features(EDA)$SCR_count,
    SCR_mean_amp = compute_scr_features(EDA)$SCR_mean_amp,
    Label        = first(Label),
    .groups = "drop"
  )




# HR (Bangle)
hr_task <- hr_data %>%
  group_by(Participant, Task) %>%
  summarise(
    HR_bangle_median = median(HR, na.rm = TRUE),
    HR_conf_mean     = mean(Confidence, na.rm = TRUE),
    Label            = first(Label),
    .groups = "drop"
  )

# # IBI (Empatica)
# ibi_task <- ibi_data %>%
#   group_by(Participant, Task) %>%
#   summarise(
#     Mean_IBI    = mean(IBI, na.rm = TRUE),
#     SDNN        = ibi_to_sdnn(IBI),
#     RMSSD_IBI   = compute_rmssd_from_ibi(IBI),
#     Mean_HR_IBI = ibi_to_mean_hr(IBI),
#     Label       = first(Label),
#     .groups = "drop"
#   )

# ECG (Shimmer)
ecg_task <- ecg_data %>%
  group_by(Participant, Task) %>%
  summarise(
    RMSSD_ECG = {
      cols <- c("ECG LL-RA CAL","ECG LA-RA CAL","ECG Vx-RL CAL")
      col_present <- cols[cols %in% names(cur_data_all())]
      if (length(col_present) == 0) NA_real_
      else {
        sig <- unlist(cur_data_all()[, col_present[1]])
        compute_rmssd_from_ecg(sig, sampling_rate = 250)
      }
    },
    Label = first(Label),
    .groups = "drop"
  )


# Merge realistic features


# glm_data_industry <- eda_task %>%
#   full_join(hr_task,  by = c("Participant","Task","Label")) %>%
#   full_join(ibi_task, by = c("Participant","Task","Label")) %>%
#   full_join(ecg_task, by = c("Participant","Task","Label"))
# 
# print(head(glm_data_industry))
```


```{r}
# ----------------------------
# Merge features (EDA + HR + ECG only)
# ----------------------------

glm_data_industry <- eda_task %>%
  full_join(hr_task,  by = c("Participant","Task")) %>%
  full_join(ecg_task, by = c("Participant","Task"))



# ----------------------------
# Inspect results
# ----------------------------
print(dim(glm_data_industry))   # rows x columns
print(head(glm_data_industry))

```




STARTING ANALYSIS

```{r}
baseline_rows <- glm_data_industry %>%
  filter(Task == "Baseline")

# Inspect
print(baseline_rows)

```

Getting only Delta
```{r}
library(dplyr)
names(glm_data_industry)


baseline_task <- glm_data_industry %>%
  filter(Task == "Baseline")

glm_data_norm <- glm_data_industry %>%
  filter(Task != "Baseline") %>%
  left_join(
    baseline_task %>% dplyr::select(-Task),   # force dplyr::select
    by = "Participant",
    suffix = c("", "_baseline")
  )


glm_data_norm <- glm_data_industry %>%
  filter(Task != "Baseline") %>%   # keep only task rows
  left_join(baseline_task, by = "Participant", suffix = c("", "_baseline"))


#Subtract baseline values from task values:
glm_data_norm <- glm_data_norm %>%
  mutate(
    EDA_mean_delta   = EDA_mean   - EDA_mean_baseline,
    EDA_median_delta = EDA_median - EDA_median_baseline,
    EDA_sd_delta     = EDA_sd     - EDA_sd_baseline,
    SCR_count_delta  = SCR_count  - SCR_count_baseline,
    SCR_amp_delta    = SCR_mean_amp - SCR_mean_amp_baseline,
    HR_median_delta  = HR_median  - HR_median_baseline,
    TEMP_median_delta = TEMP_median - TEMP_median_baseline,
    ACC_vm_mean_delta = ACC_vm_mean - ACC_vm_mean_baseline,
    ACC_vm_sd_delta   = ACC_vm_sd   - ACC_vm_sd_baseline,
    HR_bangle_delta   = HR_bangle_median - HR_bangle_median_baseline,
    HR_conf_delta     = HR_conf_mean - HR_conf_mean_baseline,
    RMSSD_ECG_delta   = RMSSD_ECG - RMSSD_ECG_baseline
  )


glm_data_norm <- glm_data_norm[, !(names(glm_data_norm) %in% "Task_baseline")]
colnames(glm_data_norm)


```

Training data, vs Test Data
```{r}

nrow(glm_model_data)
# Load libraries
library(dplyr)
library(caret)
library(zoo)

# -------------------------------
# Step 1: Keep only deltas + Label
# -------------------------------
glm_model_data <- glm_data_norm %>%
  dplyr::select(Label, ends_with("_delta"))

# -------------------------------
# Step 2: Interpolate + Impute missing values
# -------------------------------
glm_model_data_interp <- glm_model_data %>%
  # First interpolate internal gaps
  mutate(across(ends_with("_delta"), ~ na.approx(.x, na.rm = FALSE))) %>%
  # Then impute any remaining NAs (leading/trailing or structural) with column median
  mutate(across(ends_with("_delta"),
                ~ ifelse(is.na(.x), median(.x, na.rm = TRUE), .x)))

#Drop Label missing data
glm_model_data_interp <- glm_model_data_interp %>%
  filter(!is.na(Label))

glm_model_data_interp$Label <- factor(glm_model_data_interp$Label,
                                      levels = c("NO-STRESS", "STRESS"),
                                      labels = c("NOSTRESS", "STRESS"))


# -------------------------------
# Step 3: Optional train/test split
# -------------------------------
set.seed(123)  # reproducibility
train_idx <- sample(seq_len(nrow(glm_model_data_interp)), size = 0.7 * nrow(glm_model_data_interp))
train_data <- glm_model_data_interp[train_idx, ]
test_data  <- glm_model_data_interp[-train_idx, ]


# -------------------------------
# Step 4: Cross-validation setup
# -------------------------------
ctrl <- trainControl(method = "cv", number = 10,
                     classProbs = TRUE,
                     summaryFunction = twoClassSummary)

# -------------------------------
# Step 5: Train logistic regression
# -------------------------------
model <- train(Label ~ ., 
               data = glm_model_data_interp,
               method = "glm",
               family = binomial,
               trControl = ctrl,
               metric = "ROC")

# -------------------------------
# Step 6: Inspect results
# -------------------------------
print(model)
summary(model)


#sum(is.na(glm_model_data_interp))

```
Random Forest
```{r}
model_rf <- train(Label ~ ., 
                  data = glm_model_data_interp,
                  method = "rf",
                  trControl = ctrl,
                  metric = "ROC")
print(model_rf)

```

Gradient Booster
```{r}
model_gbm <- train(Label ~ ., 
                   data = glm_model_data_interp,
                   method = "gbm",
                   trControl = ctrl,
                   metric = "ROC",
                   verbose = FALSE)
print(model_gbm)

```



```{r}
#Support Vector Machines (SVM)
model_svm <- train(Label ~ ., 
                   data = glm_model_data_interp,
                   method = "svmRadial",
                   trControl = ctrl,
                   metric = "ROC")
print(model_svm)

```


```{r}
#Regularized Logistic Regression (GLMNET)
model_glmnet <- train(Label ~ ., 
                      data = glm_model_data_interp,
                      method = "glmnet",
                      trControl = ctrl,
                      metric = "ROC")
print(model_glmnet)

```


```{r}
#XGBoost (Extreme Gradient Boosting)
# model_xgb <- train(Label ~ ., 
#                    data = glm_model_data_interp,
#                    method = "xgbTree",
#                    trControl = ctrl,
#                    metric = "ROC")
# print(model_xgb)

```


Diagnostics
```{r}
library(caret)
library(pROC)

# Collect models into a list
results <- resamples(list(
  Logistic = model,
  RF = model_rf,
  GBM = model_gbm,
  SVM = model_svm,
  GLMNET = model_glmnet
  #XGB = model_xgb
))

# Summary comparison
summary(results)

# Boxplot comparison of ROC
bwplot(results, metric = "ROC")

# -------------------------------
# Plot ROC curves for each model
# -------------------------------

roc_log <- roc(response = test_data$Label,
               predictor = predict(model, test_data, type = "prob")[, "STRESS"],
               levels = c("NOSTRESS", "STRESS"))

roc_rf <- roc(response = test_data$Label,
              predictor = predict(model_rf, test_data, type = "prob")[, "STRESS"],
              levels = c("NOSTRESS", "STRESS"))

roc_gbm <- roc(response = test_data$Label,
               predictor = predict(model_gbm, test_data, type = "prob")[, "STRESS"],
               levels = c("NOSTRESS", "STRESS"))

roc_svm <- roc(response = test_data$Label,
               predictor = predict(model_svm, test_data, type = "prob")[, "STRESS"],
               levels = c("NOSTRESS", "STRESS"))

roc_glmnet <- roc(response = test_data$Label,
                  predictor = predict(model_glmnet, test_data, type = "prob")[, "STRESS"],
                  levels = c("NOSTRESS", "STRESS"))

# roc_xgb <- roc(response = test_data$Label,
#                predictor = predict(model_xgb, test_data, type = "prob")[, "STRESS"],
#                levels = c("NOSTRESS", "STRESS"))

# Plot all ROC curves together
plot(roc_log, col = "blue", lwd = 2, main = "ROC Curves: Logistic, RF, GBM, SVM, GLMNET, XGB")
plot(roc_rf, col = "red", lwd = 2, add = TRUE)
plot(roc_gbm, col = "green", lwd = 2, add = TRUE)
plot(roc_svm, col = "purple", lwd = 2, add = TRUE)
plot(roc_glmnet, col = "orange", lwd = 2, add = TRUE)
#plot(roc_xgb, col = "brown", lwd = 2, add = TRUE)

# Add legend with AUC values
legend("bottomright",
       legend = c(
         paste("Logistic (AUC =", round(auc(roc_log), 3), ")"),
         paste("Random Forest (AUC =", round(auc(roc_rf), 3), ")"),
         paste("GBM (AUC =", round(auc(roc_gbm), 3), ")"),
         paste("SVM (AUC =", round(auc(roc_svm), 3), ")"),
         paste("GLMNET (AUC =", round(auc(roc_glmnet), 3), ")")
         #paste("XGB (AUC =", round(auc(roc_xgb), 3), ")")
       ),
       col = c("blue", "red", "green", "purple", "orange", "brown"),
       lwd = 2)


```

GLM seems to be the best model as there are science of overfitting in Random Forest, GBM, and SVM

























THE MODEL I FINALLY USED FOR TRAINING DATA IS THIS
USING THE TIMESTAMP



```{r}
library(dplyr)
library(lubridate)

# -------------------------------
# Step 1: Define window size
# -------------------------------
window_size <- 10  # seconds

# -------------------------------
# Step 2: Convert timestamps
# -------------------------------
eda_data_1 <- eda_data %>% mutate(Timestamp = as.POSIXct(Timestamp, tz = "UTC"))
hr_data_1  <- hr_data  %>% mutate(Timestamp = as.POSIXct(Timestamp, tz = "UTC"))
ecg_data <- ecg_data %>%
  mutate(Timestamp = as.POSIXct(Timestamp,
                                format = "%Y-%m-%d %H:%M:%OS",
                                tz = "UTC"))


# -------------------------------
# Step 3: Add window IDs
# -------------------------------
add_window_id <- function(df, window_size) {
  df %>%
    group_by(Participant, Task) %>%
    mutate(
      rel_time = as.numeric(difftime(Timestamp, min(Timestamp), units = "secs")),
      window_id = floor(rel_time / window_size)
    ) %>%
    ungroup()
}

eda_data_1 <- add_window_id(eda_data, window_size)
hr_data_1  <- add_window_id(hr_data, window_size)
ecg_data_1 <- add_window_id(ecg_data, window_size)

# -------------------------------
# Step 4: Aggregate features per window
# -------------------------------

# EDA features
eda_task_1 <- eda_data_1 %>%
  group_by(Participant, Task, window_id) %>%
  summarise(
    EDA_median_1   = median(EDA, na.rm = TRUE),
    EDA_mean_1     = mean(EDA, na.rm = TRUE),
    EDA_sd_1       = sd(EDA, na.rm = TRUE),
    ACC_vm_mean_1  = mean(sqrt(ACC_X^2 + ACC_Y^2 + ACC_Z^2), na.rm = TRUE),
    ACC_vm_sd_1    = sd(sqrt(ACC_X^2 + ACC_Y^2 + ACC_Z^2), na.rm = TRUE),
    HR_median_1    = median(HR, na.rm = TRUE),
    TEMP_median_1  = median(TEMP, na.rm = TRUE),
    SCR_count_1    = compute_scr_features(EDA)$SCR_count,
    SCR_mean_amp_1 = compute_scr_features(EDA)$SCR_mean_amp,
    Label          = first(Label),
    .groups = "drop"
  )

# HR features
hr_task_1 <- hr_data_1 %>%
  group_by(Participant, Task, window_id) %>%
  summarise(
    HR_bangle_median_1 = median(HR, na.rm = TRUE),
    HR_conf_mean_1     = mean(Confidence, na.rm = TRUE),
    Label              = first(Label),
    .groups = "drop"
  )

# ECG features
ecg_task_1 <- ecg_data_1 %>%
  group_by(Participant, Task, window_id) %>%
  summarise(
    RMSSD_ECG_1 = {
      cols <- c("ECG LL-RA CAL","ECG LA-RA CAL","ECG Vx-RL CAL")
      col_present <- cols[cols %in% names(cur_data_all())]
      if (length(col_present) == 0) NA_real_
      else {
        sig <- unlist(cur_data_all()[, col_present[1]])
        compute_rmssd_from_ecg(sig, sampling_rate = 250)
      }
    },
    Label = first(Label),
    .groups = "drop"
  )

# -------------------------------
# Step 5: Merge all features
# -------------------------------
all_features_1 <- eda_task_1 %>%
  full_join(hr_task_1,  by = c("Participant", "Task", "window_id", "Label")) %>%
  full_join(ecg_task_1, by = c("Participant", "Task", "window_id", "Label"))

```


```{r}
 sum(is.na(all_features_1$Label))
# 
# sum(is.na(hr_task$HR_conf_mean))
# 
# nrow(hr_task) 
# nrow(glm_data_industry)
```







```{r}
library(dplyr)

all_features_2 <- all_features_1 %>%
  group_by(Participant, Task) %>%
  mutate(
    Label = ifelse(Task == "Baseline", NA, first(na.omit(Label)))
  ) %>%
  ungroup()

#View(all_features_2)

```

```{r}
baseline_rows <- all_features_2 %>%
  filter(Task == "Baseline")

# Inspect
print(baseline_rows)

```


Getting only Delta
```{r}
library(dplyr)
names(all_features_2)

# all_features_1 %>%
#    distinct(SCR_count_1)

baseline_task_2 <- all_features_2 %>%
  filter(Task == "Baseline")

glm_data_norm_2 <- all_features_2 %>%
  filter(Task != "Baseline") %>%
  left_join(baseline_task_2 %>% select(-Task),
            by = c("Participant", "window_id"),
            suffix = c("", "_baseline"))



glm_data_norm_2 <- all_features_2 %>%
  filter(Task != "Baseline") %>%   # keep only task rows
  left_join(baseline_task_2, by = "Participant", suffix = c("", "_baseline"))


#Subtract baseline values from task values:
glm_data_norm_2 <- glm_data_norm_2 %>%
  mutate(
    EDA_mean_delta    = EDA_mean_1    - EDA_mean_1_baseline,
    EDA_median_delta  = EDA_median_1  - EDA_median_1_baseline,
    EDA_sd_delta      = EDA_sd_1      - EDA_sd_1_baseline,
    SCR_count_delta   = SCR_count_1   - SCR_count_1_baseline,
    SCR_amp_delta     = SCR_mean_amp_1 - SCR_mean_amp_1_baseline,
    HR_median_delta   = HR_median_1   - HR_median_1_baseline,
    TEMP_median_delta = TEMP_median_1 - TEMP_median_1_baseline,
    ACC_vm_mean_delta = ACC_vm_mean_1 - ACC_vm_mean_1_baseline,
    ACC_vm_sd_delta   = ACC_vm_sd_1   - ACC_vm_sd_1_baseline,
    HR_bangle_delta   = HR_bangle_median_1 - HR_bangle_median_1_baseline,
    HR_conf_delta     = HR_conf_mean_1 - HR_conf_mean_1_baseline,
    RMSSD_ECG_delta   = RMSSD_ECG_1   - RMSSD_ECG_1_baseline
  )

# Now drop the baseline Task column separately
glm_data_norm_2 <- glm_data_norm_2[, !(names(glm_data_norm_2) %in% "Task_baseline")]


#colnames(glm_data_norm_2)
#colnames(all_features_2)

```

Training data, vs Test Data
```{r}
library(dplyr)
library(caret)
library(zoo)
library(forcats)

# Step 1: Baseline subset
baseline_task_2 <- all_features_2 %>%
  filter(Task == "Baseline")

# Step 2: Join baseline to task rows (only once!)
glm_data_norm_2 <- all_features_2 %>%
  filter(Task != "Baseline") %>%
  left_join(baseline_task_2 %>% select(-Task),
            by = c("Participant", "window_id"),
            suffix = c("", "_baseline"))

# Step 3: Subtract baseline values
glm_data_norm_2 <- glm_data_norm_2 %>%
  mutate(
    EDA_mean_delta    = EDA_mean_1    - EDA_mean_1_baseline,
    EDA_median_delta  = EDA_median_1  - EDA_median_1_baseline,
    EDA_sd_delta      = EDA_sd_1      - EDA_sd_1_baseline,
    SCR_count_delta   = SCR_count_1   - SCR_count_1_baseline,
    SCR_amp_delta     = SCR_mean_amp_1 - SCR_mean_amp_1_baseline,
    HR_median_delta   = HR_median_1   - HR_median_1_baseline,
    TEMP_median_delta = TEMP_median_1 - TEMP_median_1_baseline,
    ACC_vm_mean_delta = ACC_vm_mean_1 - ACC_vm_mean_1_baseline,
    ACC_vm_sd_delta   = ACC_vm_sd_1   - ACC_vm_sd_1_baseline,
    HR_bangle_delta   = HR_bangle_median_1 - HR_bangle_median_1_baseline,
    HR_conf_delta     = HR_conf_mean_1 - HR_conf_mean_1_baseline,
    RMSSD_ECG_delta   = RMSSD_ECG_1   - RMSSD_ECG_1_baseline
  ) 

# Step 4: Training data prep
glm_model_data_2 <- glm_data_norm_2 %>%
  select(Label, ends_with("_delta"))

glm_model_data_interp_2 <- glm_model_data_2 %>%
  mutate(across(ends_with("_delta"), ~ zoo::na.approx(.x, na.rm = FALSE))) %>%
  mutate(across(ends_with("_delta"),
                ~ ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))) %>%
  filter(!is.na(Label))

# Fix Label factor levels
glm_model_data_interp_2$Label <- forcats::fct_recode(glm_model_data_interp_2$Label,
                                                     NOSTRESS = "NO-STRESS",
                                                     STRESS   = "STRESS")

# Step 5: Train/test split
set.seed(123)
train_idx <- sample(seq_len(nrow(glm_model_data_interp_2)), size = 0.7 * nrow(glm_model_data_interp_2))
train_data_2 <- glm_model_data_interp_2[train_idx, ]
test_data_2  <- glm_model_data_interp_2[-train_idx, ]

# Step 6: Cross-validation setup
ctrl_2 <- trainControl(method = "cv", number = 10,
                       classProbs = TRUE,
                       summaryFunction = twoClassSummary)
```


```{r}
colnames(train_data_2)

# Step 7: Train logistic regression
model_2 <- train(Label ~ ., 
                 data = train_data_2,
                 method = "glm",
                 family = binomial,
                 trControl = ctrl_2,
                 metric = "ROC")

print(model_2)
summary(model_2)
```


```{r}
#Reduced Model
model_3 <- train(Label ~ EDA_mean_delta + EDA_median_delta + SCR_count_delta + TEMP_median_delta + HR_bangle_delta + RMSSD_ECG_delta, 
                 data = train_data_2,
                 method = "glm",
                 family = binomial,
                 trControl = ctrl_2,
                 metric = "ROC")
print(model_3)
summary(model_3)

```
Random Forest
```{r}
model_rf_2 <- train(Label ~ ., 
                  data = train_data_2,
                  method = "rf",
                  trControl = ctrl_2,
                  metric = "ROC")
print(model_rf_2)

```

Gradient Booster
```{r}
model_gbm_2 <- train(Label ~ ., 
                   data = train_data_2,
                   method = "gbm",
                   trControl = ctrl_2,
                   metric = "ROC",
                   verbose = FALSE)
print(model_gbm_2)

```





```{r}
#Support Vector Machines (SVM)
model_svm_2 <- train(Label ~ ., 
                   data = train_data_2,
                   method = "svmRadial",
                   trControl = ctrl_2,
                   metric = "ROC")
print(model_svm_2)

```


```{r}
#Regularized Logistic Regression (GLMNET)
model_glmnet_2 <- train(Label ~ ., 
                      data = train_data_2,
                      method = "glmnet",
                      trControl = ctrl_2,
                      metric = "ROC")
print(model_glmnet_2)

```


```{r}
#XGBoost (Extreme Gradient Boosting)
# model_xgb_2 <- train(Label ~ ., 
#                    data = train_data_2,
#                    method = "xgbTree",
#                    trControl = ctrl_2,
#                    metric = "ROC")
# print(model_xgb)

```


Diagnostics
```{r}
library(caret)
library(pROC)

# Collect models into a list
results <- resamples(list(
  Logistic = model_2,
  RF = model_rf_2,
  GBM = model_gbm_2,
  SVM = model_svm_2,
  GLMNET = model_glmnet_2
  #XGB = model_xgb
))

# Summary comparison
summary(results)

# Boxplot comparison of ROC
bwplot(results, metric = "ROC")

# -------------------------------
# Plot ROC curves for each model
# -------------------------------

roc_log <- roc(response = test_data_2$Label,
               predictor = predict(model_2, test_data_2, type = "prob")[, "STRESS"],
               levels = c("NOSTRESS", "STRESS"))

roc_rf <- roc(response = test_data_2$Label,
              predictor = predict(model_rf_2, test_data_2, type = "prob")[, "STRESS"],
              levels = c("NOSTRESS", "STRESS"))

roc_gbm <- roc(response = test_data_2$Label,
               predictor = predict(model_gbm_2, test_data_2, type = "prob")[, "STRESS"],
               levels = c("NOSTRESS", "STRESS"))

roc_svm <- roc(response = test_data_2$Label,
               predictor = predict(model_svm_2, test_data_2, type = "prob")[, "STRESS"],
               levels = c("NOSTRESS", "STRESS"))

roc_glmnet <- roc(response = test_data_2$Label,
                  predictor = predict(model_glmnet_2, test_data_2, type = "prob")[, "STRESS"],
                  levels = c("NOSTRESS", "STRESS"))

# roc_xgb <- roc(response = test_data_2$Label,
#                predictor = predict(model_xgb, test_data, type = "prob")[, "STRESS"],
#                levels = c("NOSTRESS", "STRESS"))

# Plot all ROC curves together
plot(roc_log, col = "blue", lwd = 2, main = "ROC Curves: Logistic, RF, GBM, SVM, GLMNET")
plot(roc_rf, col = "red", lwd = 2, add = TRUE)
plot(roc_gbm, col = "green", lwd = 2, add = TRUE)
plot(roc_svm, col = "purple", lwd = 2, add = TRUE)
plot(roc_glmnet, col = "orange", lwd = 2, add = TRUE)
#plot(roc_xgb, col = "brown", lwd = 2, add = TRUE)

# Add legend with AUC values
legend("bottomright",
       legend = c(
         paste("Logistic (AUC =", round(auc(roc_log), 3), ")"),
         paste("Random Forest (AUC =", round(auc(roc_rf), 3), ")"),
         paste("GBM (AUC =", round(auc(roc_gbm), 3), ")"),
         paste("SVM (AUC =", round(auc(roc_svm), 3), ")"),
         paste("GLMNET (AUC =", round(auc(roc_glmnet), 3), ")")
         #paste("XGB (AUC =", round(auc(roc_xgb), 3), ")")
       ),
       col = c("blue", "red", "green", "purple", "orange", "brown"),
       lwd = 2)


```





















# DASHBOARD

```{r}
# ============================
# DASHBOARD
# ============================

library(shiny)
library(ggplot2)
library(DT)

# Load your trained Random Forest model
# Make sure you have saved it earlier with:
saveRDS(model_rf_2, "rf_model_2.rds")
model_rf_2 <- readRDS("rf_model_2.rds")

# Define UI
ui <- fluidPage(
  titlePanel("Stress Prediction Dashboard"),
  
  sidebarLayout(
    sidebarPanel(
      h4("Manual Input (Single Participant)"),
      numericInput("EDA_mean_delta", "EDA Mean Δ", value = 0),
      numericInput("TEMP_median_delta", "Temp Median Δ", value = 0),
      numericInput("HR_median_delta", "HR Median Δ", value = 0),
      numericInput("ACC_vm_mean_delta", "ACC Mean Δ", value = 0),
      numericInput("RMSSD_ECG_delta", "RMSSD ECG Δ", value = 0),
      actionButton("predict", "Predict Stress"),
      hr(),
      
      h4("Batch Prediction (CSV Upload)"),
      fileInput("file", "Upload CSV File", accept = c(".csv")),
      helpText("CSV should contain columns: 
               EDA_mean_delta, TEMP_median_delta, HR_median_delta, 
               ACC_vm_mean_delta, RMSSD_ECG_delta")
    ),
    
    mainPanel(
      h3("Single Participant Prediction"),
      textOutput("prediction"),
      plotOutput("probPlot"),
      hr(),
      h3("Batch Predictions"),
      DTOutput("batchTable")
    )
  )
)

# Define server logic
server <- function(input, output) {
  
  # Single participant prediction
  observeEvent(input$predict, {
    newdata <- data.frame(
      EDA_mean_delta    = input$EDA_mean_delta,
      TEMP_median_delta = input$TEMP_median_delta,
      HR_median_delta   = input$HR_median_delta,
      ACC_vm_mean_delta = input$ACC_vm_mean_delta,
      RMSSD_ECG_delta   = input$RMSSD_ECG_delta
    )
    
    prob <- predict(model_rf_2, newdata, type = "prob")
    class <- predict(model_rf_2, newdata)
    
    output$prediction <- renderText({
      paste("Predicted Class:", as.character(class))
    })
    
    output$probPlot <- renderPlot({
      df <- data.frame(Class = colnames(prob), Probability = as.numeric(prob[1,]))
      ggplot(df, aes(x = Class, y = Probability, fill = Class)) +
        geom_bar(stat = "identity") +
        ylim(0,1) +
        theme_minimal() +
        ggtitle("Prediction Probabilities")
    })
  })
  
  # Batch prediction from CSV
  observeEvent(input$file, {
    req(input$file)
    data <- read.csv(input$file$datapath)
    
    required_cols <- c("EDA_mean_delta", "TEMP_median_delta", 
                       "HR_median_delta", "ACC_vm_mean_delta", "RMSSD_ECG_delta")
    missing_cols <- setdiff(required_cols, names(data))
    
    if (length(missing_cols) > 0) {
      output$batchTable <- renderDT({
        datatable(data.frame(Error = paste("Missing columns:", paste(missing_cols, collapse = ", "))))
      })
    } else {
      classes <- predict(model_rf_2, data)
      probs <- predict(model_rf_2, data, type = "prob")
      
      results <- cbind(data, Predicted_Class = classes, probs)
      
      output$batchTable <- renderDT({
        datatable(results, options = list(pageLength = 10))
      })
    }
  })
}

# Run the app
shinyApp(ui = ui, server = server)

```

